PInSoRo: A Dataset for Deep-learning of Human-Robot Social Interactions

### 2017-06-27 paper.tex
WIP section on annotations of social behaviours

\subsubsection{Initial Dataset Analysis}

@@

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{analysis}
    \caption{Screenshot of the interaction analysis tool: faces of the two
    children are recorded, as well as any interaction occuring on the
    interactive table.}
    \label{fig|analysis}
\end{figure}

@@

\subsection{Specific research questions}

\begin{figure}
\centering

\resizebox{0.8\linewidth}{!}{%
\begin{tikzpicture}[
                font=\sffamily,
                >=latex,
                every edge/.style={draw, very thick},
                node/.style={draw, rounded corners, align=center, inner sep=5pt, fill=black!20},
                label/.style={midway, align=center, font=\scriptsize\sffamily, fill=white}]

    %%% NODES
    \node [node] (mentalrepresentations) {Mental Representations};
    \node [above left=of mentalrepresentations] (gameactions) {\it game actions};
    \node [node, above=of gameactions] (gamedynamics) {Game dynamics};
    \node [above right=of mentalrepresentations] (socialactions) {\it social actions};
    \node [node, above=of socialactions ] (socialdynamics) {Social Dynamics};

    %%% CONNECTIONS
    \path (gamedynamics) edge [<->, dashed] node[label, above] {?}(socialdynamics);
    \path (gamedynamics) edge [<-, bend right] node[label] {mediate}(gameactions);
    \path (socialactions) edge [->, bend left] node[label] {reflect}(mentalrepresentations);
    \path (socialactions) edge [->, dashed] node[label,above] {?}(gamedynamics);
    \path (gameactions) edge [->, dashed] node[label,above] {?}(socialdynamics);
    \path (gameactions) edge [->, bend right] node[label] {reflect}(mentalrepresentations);
    \path (socialdynamics) edge [<-, bend left] node[label] {shape}(socialactions);

\end{tikzpicture}
}
\label{fig|researchquestions}
\caption{Game dynamics, social dynamics and mental representations are linked
    with each other through social actions (implicit and explicit communication)
    and actions on the environment (mainly game actions)}
\end{figure}

The mechanisms underlying the social interactions happening during free play
raise important questions for social robotics.

>>>>

\subsection{Annotations of Social Behaviours}

\begin{figure}
    \centering
    \includegraphics[width=0.8\linewidth]{analysis}
    \caption{Screenshot of the interaction analysis tool: key record information
    are played back in a synchronised (faces and audio of the two children,
    interaction occuring on the interactive table, etc.) while the human coder
    annotate the record timeline with social situations of interest.}
    \label{fig|analysis}
\end{figure}

@@

Słowinski’s Individual Motor Signature
(for behavioural alignment), Anderson's~\cite{anderson2004social} coding of children’s free-play
interactions,

\cite{olswang2006reliability}

@@

\subsection{Specific research questions}
%
%\begin{figure}
%\centering
%
%\resizebox{0.8\linewidth}{!}{%
%\begin{tikzpicture}[
%                font=\sffamily,
%                >=latex,
%                every edge/.style={draw, very thick},
%                node/.style={draw, rounded corners, align=center, inner sep=5pt, fill=black!20},
%                label/.style={midway, align=center, font=\scriptsize\sffamily, fill=white}]
%
%    %%% NODES
%    \node [node] (mentalrepresentations) {Mental Representations};
%    \node [above left=of mentalrepresentations] (gameactions) {\it game actions};
%    \node [node, above=of gameactions] (gamedynamics) {Game dynamics};
%    \node [above right=of mentalrepresentations] (socialactions) {\it social actions};
%    \node [node, above=of socialactions ] (socialdynamics) {Social Dynamics};
%
%    %%% CONNECTIONS
%    \path (gamedynamics) edge [<->, dashed] node[label, above] {?}(socialdynamics);
%    \path (gamedynamics) edge [<-, bend right] node[label] {mediate}(gameactions);
%    \path (socialactions) edge [->, bend left] node[label] {reflect}(mentalrepresentations);
%    \path (socialactions) edge [->, dashed] node[label,above] {?}(gamedynamics);
%    \path (gameactions) edge [->, dashed] node[label,above] {?}(socialdynamics);
%    \path (gameactions) edge [->, bend right] node[label] {reflect}(mentalrepresentations);
%    \path (socialdynamics) edge [<-, bend left] node[label] {shape}(socialactions);
%
%\end{tikzpicture}
%}
%\label{fig|researchquestions}
%\caption{Game dynamics, social dynamics and mental representations are linked
%    with each other through social actions (implicit and explicit communication)
%    and actions on the environment (mainly game actions)}
%\end{figure}
%
%The mechanisms underlying the social interactions happening during free play
%raise important questions for social robotics.
